Kommunikationsprotokolle für VANETs

### 2021-02-05 paper.tex
Resize table Comment redundant subsections

\subsection{Persistance-Based Protocols}

\subsection{Multihop Vehicular Broadcast (MHVB)}

\subsection{Emergency Message Dissemination with ACK-Overhearing Based Retransmission (EMDOR)}

\subsection{Distributed Fair Power Adjustment Protocol (D-FPAV)}

\subsection{Receiver Consensus (ReC)}

\subsection{DPP und OPERA}

\subsection{Binary-Partition-Assisted Broadcast (BPAB)}

\subsection{Track Detection und Distance Defer Transmission Protocols (TRADE und DDT)}

\subsection{Connection-Based Restricted Forwarding (CBRF)}

\subsection{Distributed Vehicular Broadcast (DV-CAST)}

\subsection{Vehicle Density-Based Emergency Broadcasting (VDEB)}

\subsection{Topology-Assisted Geo-Opportunistic Routing (TO-GO)}

\subsection{Distance-Aware Epidemic Routing (DAER)}
\subsection{Connectivity-Aware Routing (CAR)}

\subsection{Delay-Bounded Routing in VANETs (D-Greedy)}
\subsection{Vehicle-Assisted Data Delivery in VANETs (VADD)}
\subsection{Trajectory-Based Data Forwarding for Light-Traffic in VANETs (TBD)}
\subsection{Static-Node-Assisted Adaptive Routing Protocol in VANETs (SADV)}
\subsection{Location- and Delay-Aware Cross-Layer Communication (LD-CROP)}
\subsection{Geopgraphical Opportunistic Routing (GeoOpps)}
\subsection{Road-Based Vehicular Traffic Routing (RBVT)}
\subsection{Improved Greedy Traffic-Aware Routing Protocol (GyTAR)}
\subsection{Acces-Overlay Routing by Two-Phase Routing Protocol (TOPO)}

@@

\begin{table}[]
  \begin{tabular}{llllllllll}
    Protokoll                     & Problem Statement     & Transmission Dimension    & Neighbor Knowledge     & Acknowledgement     & Starting Forwarder Selection    & Compete to Retransmit & Connectivity & Urgency & Message Content \\
    \hline
    Probabilistic, naive flooding & G        & 2D & NN    & NA & AA     & NC       & IC    & RO & FM \\
    Middle                        & G        & 1D & NN    & NA & IA     & TD-D     & AC    & RO & FA \\
    ackPBSM                       & G        & 2D & NP    & BA & LA, NE & TD-D     & IC    & RO & FM \\
    Persistence                   & G        & 1D & NN    & PA & IA     & TD-D     & AC    & RO & FM \\
    MHVB                          & G        & 1D & NN    & PA & NE     & TD-D     & AC    & TC & FM \\
    EMDOR                         & G        & 1D & NN    & BA & IA, LA & TD-D     & AC    & TC & FA \\
    EMDV                          & G        & 2D & NP    & RE & IA     & TD-D     & AC    & TC & FA \\
    ReC                           & G        & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    OPERA                         & R-SS     & 1D & NP    & BA & LA, NE & X        & IC    & TC & FM \\
    BPAB                          & R-SS     & 1D & NN    & PA & NE     & BB, TD-R & AC/IC & TC & FA \\
    TRADE/DDT                     & R-SS     & 1D & NP/NN & NA & IA     & TD-D     & AC    & RO & FA \\
    CBRF                          & R-SS     & 1D & NN    & BA & IA     & TD-R     & AC    & TC & FA \\
    DDP                           & R-SS     & 1D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    DV-CAST                       & R-SS     & 1D & NP    & PA & IA     & TD-D     & AC    & RO & FM \\
    VDEB                          & R-SS     & 1D & NP    & BA & I      & TD-D     & AC    & TC & FA \\
    TOGO                          & R-LS     & 1D & NP    & BA & IA     & TD-D     & IC    & RO & FM \\
    DAER                          & R-FD, LS & 2D & NP    & BA & IA     & TD-D     & AC    & RO & FM \\
    CAR                           & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FM \\
    D-greedy                      & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    VADD                          & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    TBD                           & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & TC & FM \\
    SADV                          & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    LD-CROP                       & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FM \\
    GeOpps                        & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FA \\
    RBVT                          & R-FD, LS & 2D & NP    & BA & IA     & TD-D     & AC    & RO & FA \\
    GyTAR                         & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & RO & FA \\
    TOPO                          & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FA
  \end{tabular}
  \caption{Übersicht über verschiede Kommunikationsprotokolle für VANETs\cite{conti2013mobile}}
  \label{table:1}
\end{table}

>>>>

%\subsection{Persistance-Based Protocols}
%\subsection{Multihop Vehicular Broadcast (MHVB)}
%\subsection{Emergency Message Dissemination with ACK-Overhearing Based Retransmission (EMDOR)}
%\subsection{Distributed Fair Power Adjustment Protocol (D-FPAV)}
%\subsection{Receiver Consensus (ReC)}
%\subsection{DPP und OPERA}
%\subsection{Binary-Partition-Assisted Broadcast (BPAB)}
%\subsection{Track Detection und Distance Defer Transmission Protocols (TRADE und DDT)}
%\subsection{Connection-Based Restricted Forwarding (CBRF)}
%\subsection{Distributed Vehicular Broadcast (DV-CAST)}
%\subsection{Vehicle Density-Based Emergency Broadcasting (VDEB)}
%\subsection{Topology-Assisted Geo-Opportunistic Routing (TO-GO)}
%\subsection{Distance-Aware Epidemic Routing (DAER)}
%\subsection{Connectivity-Aware Routing (CAR)}
%\subsection{Delay-Bounded Routing in VANETs (D-Greedy)}
%\subsection{Vehicle-Assisted Data Delivery in VANETs (VADD)}
%\subsection{Trajectory-Based Data Forwarding for Light-Traffic in VANETs (TBD)}
%\subsection{Static-Node-Assisted Adaptive Routing Protocol in VANETs (SADV)}
%\subsection{Location- and Delay-Aware Cross-Layer Communication (LD-CROP)}
%\subsection{Geopgraphical Opportunistic Routing (GeoOpps)}
%\subsection{Road-Based Vehicular Traffic Routing (RBVT)}
%\subsection{Improved Greedy Traffic-Aware Routing Protocol (GyTAR)}
%\subsection{Acces-Overlay Routing by Two-Phase Routing Protocol (TOPO)}

@@

\resizebox{\linewidth}{!}{\begin{table}[]
  \begin{tabular}{llllllllll}
    Protokoll                     & Problem Statement     & Transmission Dimension    & Neighbor Knowledge     & Acknowledgement     & Starting Forwarder Selection    & Compete to Retransmit & Connectivity & Urgency & Message Content \\
    \hline
    Probabilistic, naive flooding & G        & 2D & NN    & NA & AA     & NC       & IC    & RO & FM \\
    Middle                        & G        & 1D & NN    & NA & IA     & TD-D     & AC    & RO & FA \\
    ackPBSM                       & G        & 2D & NP    & BA & LA, NE & TD-D     & IC    & RO & FM \\
    Persistence                   & G        & 1D & NN    & PA & IA     & TD-D     & AC    & RO & FM \\
    MHVB                          & G        & 1D & NN    & PA & NE     & TD-D     & AC    & TC & FM \\
    EMDOR                         & G        & 1D & NN    & BA & IA, LA & TD-D     & AC    & TC & FA \\
    EMDV                          & G        & 2D & NP    & RE & IA     & TD-D     & AC    & TC & FA \\
    ReC                           & G        & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    OPERA                         & R-SS     & 1D & NP    & BA & LA, NE & X        & IC    & TC & FM \\
    BPAB                          & R-SS     & 1D & NN    & PA & NE     & BB, TD-R & AC/IC & TC & FA \\
    TRADE/DDT                     & R-SS     & 1D & NP/NN & NA & IA     & TD-D     & AC    & RO & FA \\
    CBRF                          & R-SS     & 1D & NN    & BA & IA     & TD-R     & AC    & TC & FA \\
    DDP                           & R-SS     & 1D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    DV-CAST                       & R-SS     & 1D & NP    & PA & IA     & TD-D     & AC    & RO & FM \\
    VDEB                          & R-SS     & 1D & NP    & BA & I      & TD-D     & AC    & TC & FA \\
    TOGO                          & R-LS     & 1D & NP    & BA & IA     & TD-D     & IC    & RO & FM \\
    DAER                          & R-FD, LS & 2D & NP    & BA & IA     & TD-D     & AC    & RO & FM \\
    CAR                           & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FM \\
    D-greedy                      & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    VADD                          & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    TBD                           & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & TC & FM \\
    SADV                          & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FM \\
    LD-CROP                       & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FM \\
    GeOpps                        & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & TC & FA \\
    RBVT                          & R-FD, LS & 2D & NP    & BA & IA     & TD-D     & AC    & RO & FA \\
    GyTAR                         & R-LS     & 2D & NP    & BA & IA     & TD-D     & IC    & RO & FA \\
    TOPO                          & R-LS     & 2D & NP    & BA & IA     & TD-R     & IC    & RO & FA
  \end{tabular}
  \caption{Übersicht über verschiede Kommunikationsprotokolle für VANETs\cite{conti2013mobile}}
  \label{table:1}
\end{table}}
